\textbf{EECS 340: Assignment 2}

### 2020-02-02 assignment_2/article.tex
✨ Add sketch answer to Problem 1(c1).

Please refer to proof at \textbf{b1} as it provides a broader proof base on $f(n)$ regardless $f(n) \geq 1$ or not.
\section{Problem 2}

>>>>

Please refer to proof at \textbf{b1} as it provides a broader proof base on $f(n)$ regardless $f(n) \geq 1$ or not.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(c1) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 0$, then $log(f(n)) = O(\log(g(n))$.}

According to the defination of $O$-notation, we must have:

\begin{gather}
    \exists c, n_{0} > 0 \ \text{ s.t. } \ f(n) \leq cg(n) \ \ \ \text{for $n \geq n_{0}$}
\end{gather}

Since it is given that $\log(f(n)), \log(g(n)) \geq 0$, thus we must have:

\begin{gather}
    \log(f(n)) \leq \log(c(g(n))) \ \ \ \text{for $n \geq n_{0}$} \nonumber\\
    \Rightarrow \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$}
\end{gather}

As $c, n_{0}$ are constants, there must be a constant $c'$ s.t.

\paragraph{Case 1} Assume $\log (g(n_{0})) \neq 0$:

\begin{gather}
    c' \geq \frac{\log c}{\log (g(n_{0}))} + 1 \\
    \Rightarrow (c' -1)\log (g(n))  \ \geq \ (c' -1)\log (g(n_{0})) \ \geq \ \log c \ \ \ \text{for $n \geq n_{0}$} \\
    \exists c, n_{0} > 0 \nonumber \ \text{ s.t. } \  \\
    \log(f(n)) \ \leq \ \log c + \log(g(n)) \ \leq \  (c' -1)\log (g(n)) + \log(g(n))\ \ \ \text{for $n \geq n_{0}$} \\
    \Rightarrow \log(f(n))  \leq c'\log (g(n))
\end{gather}

Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.

\paragraph{Case 2} Assume $\log (g(n_{0})) = 0$:

Since $\log (g(n_{0})) = 0$, we shall infer that $g(n_{0}) = 1$. We may arbitrarily pick some constants $c, c'}$ where:

\begin{gather}
    \log c \leq 0 \nonumber\\
    \log c \leq (c' - 1) \cdot 0 \nonumber\\
    \log c \leq (c' - 1) \cdot \log(g(n_{0}))
\end{gather}

Since $n \geq n_{0}$ by defination, and known that $g(n) \geq 1$ due to $\log(g(n)) \geq 0$; therefore there must be $g(n) \geq g(n_{0})$. Putting this into the context of \textit{Equation 10}, we may have:

\begin{gather}
    \log(f(n)) \leq \log c + \log(g(n)) \ \ \ \text{for $n \geq n_{0}$} \nonumber \\
    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n_{0})) + \log(g(n)) \nonumber \\
    \Rightarrow \log(f(n)) \leq (c' - 1) \cdot \log(g(n)) + \log(g(n)) \nonumber \\
    \Rightarrow \log(f(n)) \leq c'\log(g(n))
\end{gather}

Thus we may conclude $log(f(n)) = O(\log(g(n))$ for this case.\newline

Since both cases reach to the conclusion of $log(f(n)) = O(\log(g(n))$, we have proven the statement to be valid.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{(c2) If $f(n) = O(g(n)), \log(f(n)) \geq 0$ and $\log(g(n)) \geq 1$, then $log(f(n)) = O(\log(g(n))$.}

\section{Problem 2}
